PK object batch mode trial

### 2023-06-27 data-raw/batchMode_trial_gpm.Rmd
Updated plot function to allow predictions from time interpolation, needs data_group call flexibility

@@

my_ndf %>%
  dplyr::select(Chemical, Species,
                dplyr::all_of(req_vars),
                dplyr::any_of(trans_vars)) %>%
  mutate(Detect = ifelse(Detect, "Detect", "Non-Detect")) %>%
  View()

@@

```{r remaining_methods}
# plot()
# 
# get_tkstats()

>>>>

my_pred2 <- predict(my_pk,
                    newdata = data.frame(Chemical = "DTXSID2021731",
                                         Species = "rat",
                                         Route = "iv",
                                         Media = "plasma",
                                         Dose = 20,
                                         Time = 1.6,
                                         Time.Units = "hours"),
                    exclude = FALSE,
                    use_scale_conc = FALSE)

@@

my_ndf %>%
  dplyr::select(Chemical, Species,
                dplyr::all_of(req_vars),
                dplyr::any_of(trans_vars)) -> my_ndf

# Time interpolation
my_ndf %>% uncount(1) %>% 
  group_by(Dose, Route, Media) %>%
  mutate(Time_trans = (max(Time)/(n() - 1))*(row_number() - 1)) %>%
  View()

@@

my_plot[[3]][[2]] %>%
  dplyr::select(Time, Dose, Route, Media, Reference) %>% View("reduced")

my_plot[[3]][[2]] %>%
  tidyr::uncount(3) %>%
  arrange(Time) %>%
  group_by(across(!starts_with("Time"))) %>% 
  mutate(Time = seq(from = min(Time),
                    to = max(Time),
                    length.out = length(Time))) %>% View()

# Testing the stat_function way
# 
my_plot$observation_plot[[2]] +
  ggplot2::stat_function(fun = \(x) {
    sqrt(1/x)
    },
    aes(linetype = "solid"),
                         inherit.aes = FALSE)

my_statfun <- ggplot2::stat_function(fun = \(x) {
    sqrt(5*x)
    },
    aes(linetype = "dotted"),
    inherit.aes = FALSE) 
my_statfun2 <- ggplot2::stat_function(fun = \(x) {
    0.5*x
    },
    aes(linetype = "solid"),
    inherit.aes = FALSE) 
# Note that we cannot add ggproto objects together! But I can make them into a list
# and add that to the main object

my_plot$observation_plot[[2]] + list(my_statfun, my_statfun2)

my_plot$observation_plot[[2]] + my_statfun +
  scale_linetype_identity()
```

```{r remaining_methods}
# plot()
# coef_sd
# logLik.pk
# get_tkstats()
